Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}

@@

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\subsubsection{Input data}

To run a KUB simulation, several input files need to be generated.
We have several metadata files (in JSON format), mesh data files (in MSH format), and
meteorological measurement files (in CSV format).
In the table \ref{tab:input-data-size-comparison}, we have listed these files
with their corresponding sizes.
In this comparison, we used New York City as the location
and a duration of one year for the simulation.
In addition, we compared the size of the input data with the size of the zone.

\begin{table}[h]
\begin{center}
  \begin{tabular}{|c|| c | c | c|} 
    \hline
    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
    \hline\hline
    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
    \hline
    gis.json & 23 M & 117M & 470 M \\
    \hline
    mesh\_lod0.msh & 17 M & 112M & 496 M \\
    \hline
    mesh\_lod1.msh & 44 M & 240M & 896 M \\
    \hline
    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
    \hline
    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
    \hline
  \end{tabular}
\end{center}
\caption{Size comparison of input data using New York city.}
\label{tab:input-data-size-comparison}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance. Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates. 
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings). The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}. Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina. They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}. This figure reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}

The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
All machines tested have an elapsed time of the same magnitude order.

>>>>

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and 
Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Gwennolé Chappron \inst{1}\orcidID{0009-0003-7588-3370} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}
\usepackage{cleveref}

@@

The Ktirio urban building workflow, see \cref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}

\end{figure}

In \cref{fig:buildings}, we illustrate the different levels of details. 
\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Vegetation Modeling}

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:

\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. 
\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}
\label{sec:benchmarking}

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance.
Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates.
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see \cref{fig:kub-hpcops}.
\Cref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}
